Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-03 popl24/intro.tex
checkpoint

>>>>

In \ref{section-minicat} we develop a new probabilistic programming
language $\minifed$ for defining synchronous distributed protocols
over the binary field. The syntax and semantics provides a succinct
account of \emph{views} and (synchronous) messaging between protocol
\emph{clients}. In this Section we consider small example protocols
including oblivious transfer, communications encryption with one-time
pads, and additive secret sharing. In Section \ref{section-pmf} we
formulate \emph{program distributions}, a formalism for expressing
dependencies between secrets and views, useful for expressing
intensional characteristics of protocols and precisely quantifying
allowable information leakage in terms of protocol outputs.
